Learning words through recursive pragmatic reasoning about other agents

### 2013-05-30 praglearn.tex
start hacking figures into shape

\documentclass{article} % For LaTeX2e
\usepackage{nips13submit_e,times}
\usepackage{hyperref}
\usepackage{url}
\usepackage{amsmath}
\usepackage{graphicx}
%\documentstyle[nips13submit_09,times,art10]{article} % For LaTeX 2.09

@@

\author{
Nathaniel Smith\thanks{...} \\
School of Informatics\\
University of Edinburgh\\
Edinburgh, Scotland, UK\\
\texttt{nsmith23@inf.ed.ac.uk} \\
\AND
Noah D. Goodman \\
Department of Psychology\\
Stanford University \\
Stanford, CA, USA \\
\texttt{ngoodman@stanford.edu} \\
\And
Michael C. Frank \\
Department of Psychology \\
Stanford University \\
Stanford, CA, USA \\
\texttt{mcfrank@stanford.edu}}

@@

To simplify matters we envision a simple world that has $w$ words and $b$ objects. The \textit{lexicon} defines the literal meaning of each word, ...

@@

\subsection{"Social anxiety" model}

@@

\begin{figure}
\centering
\includegraphics[width=5.5in]{figures/galantucci3.png}
\caption{\label{fig:glantucci} Simulations....} 
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=5.5in]{figures/horn.png}
\caption{\label{fig:horn} Simulations.} 
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=2in]{figures/pragmatic_scalar.png}
\includegraphics[width=2in]{figures/nonpragmatic_scalar.png}
\caption{\label{fig:scalar} Simulations..} 
\end{figure}

>>>>

\documentclass{article} % For LaTeX2e
\usepackage{nips13submit_e,times}
\usepackage{hyperref}
\usepackage{url}
\usepackage{amsmath}
\usepackage{graphicx}

@@

\author{
Nathaniel Smith\thanks{...} \\
School of Informatics\\
University of Edinburgh\\
Edinburgh, Scotland, UK\\
\texttt{nathaniel.smith@ed.ac.uk} \\
\AND
Noah D. Goodman \\
Department of Psychology\\
Stanford University \\
Stanford, CA, USA \\
\texttt{ngoodman@stanford.edu} \\
\And
Michael C. Frank \\
Department of Psychology \\
Stanford University \\
Stanford, CA, USA \\
\texttt{mcfrank@stanford.edu}}

@@

To simplify matters we envision a simple world that has $k$ words and $l$ objects. The \textit{lexicon} defines the literal meaning of each word, ...

extensional as marginalization over intensional

@@

\subsection{``Social anxiety'' model}

@@

\begin{figure}
\centering
\includegraphics[width=0.48\textwidth]{figures/emergence2x2-1.pdf}
\includegraphics[width=0.48\textwidth]{figures/emergence2x2-3.pdf} \\
\includegraphics[width=0.48\textwidth]{figures/emergence3x3-0.pdf}
\includegraphics[width=0.48\textwidth]{figures/emergence3x3-1.pdf} \\
\caption{\label{fig:emergence} Simulations....}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.48\textwidth]{figures/horn-emergence-0.pdf}
\includegraphics[width=0.48\textwidth]{figures/horn-emergence-1.pdf}
\caption{\label{fig:horn} Simulations.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=2in]{figures/some-all-only-pragmatic.pdf}
\includegraphics[width=2in]{figures/some-all-pragmatic+unambiguous.pdf}
\caption{\label{fig:scalar} Simulations..}
\end{figure}
